---
title: "Wisdom of crowds - Experimental results"
author: "Simon Garnier"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    css: custom.css
    fig_caption: true
    fig_width: 8
    number_sections: true
    theme: cosmo
    toc: true
    csl: plos.csl
    bibliography: library.bib
---

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(RMySQL)
library(dplyr)
library(RColorBrewer)

cbf <- brewer.pal(8, "Dark2")
```

--- 

# Open connection to database

```{r, 'con', warning=FALSE}
con <- dbConnect(MySQL(), default.file = normalizePath("../mysql.cfg"))
dat <- dbReadTable(conn = con, name = "woc") %>%
  mutate(type = factor(type, levels = c("naive", "informed")))

dat <- mutate(dat, error = abs(count - 123))
```

[Back to top]("#")

---

# Estimates distribution (naive)

```{r, 'figure_1', message=FALSE, dpi=300}
mean_naive <- mean(filter(dat, type == "naive")$count)
median_naive <- median(filter(dat, type == "naive")$count)

ggplot(filter(dat, type == "naive"), aes(x = count)) +
  geom_histogram(aes(y = ..density..), fill = cbf[8], alpha = 0.5, 
                 binwidth = diff(range(dat$count)) / 15) + 
  geom_density(size = 1) + 
  geom_vline(xintercept = 123, linetype = 2, size = 1) + 
  geom_vline(xintercept = mean_naive, color = cbf[2], size = 1) + 
  #geom_vline(xintercept = median_naive, color = cbf[3], size = 1) + 
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlab("Estimate") + ylab("Density") +
  xlim(range(dat$count))
```
<p class="caption">**Figure 1:** Figure caption.</p>

[Back to top]("#")

---

# Estimates' error distribution (naive)

```{r, 'figure_2', message=FALSE, dpi=300}
ggplot(filter(dat, type == "naive"), aes(x = error)) +
  geom_histogram(aes(y = ..density..), fill = cbf[8], alpha = 0.5, 
                 binwidth = diff(range(dat$error)) / 15) + 
  geom_density(size = 1) + 
  geom_vline(xintercept = abs(mean_naive - 123), color = cbf[2], size = 1) + 
  #geom_vline(xintercept = abs(median_naive - 123), color = cbf[3], size = 1) +
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlab("Error") + ylab("Density")
```
<p class="caption">**Figure 2:** Figure caption.</p>

Average estimate is better than `r 100 * sum(abs(mean_naive - 123) <= filter(dat, type == "naive")$error) / length(filter(dat, type == "naive")$count)` percent of the individual estimates. 

[Back to top]("#")

---

# Confidence vs error

```{r, 'figure_3', message=FALSE, dpi=300}
ggplot(filter(dat, type == "naive"), aes(x = conf, y = error)) +
  geom_point() + 
  geom_smooth(size = 1, method = "lm", color = cbf[3]) + 
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlim(0, 10) +
  xlab("Confidence") + ylab("Error")
```
<p class="caption">**Figure 3:** Figure caption.</p>

[Back to top]("#")

---

# Estimates distribution (informed)

```{r, 'figure_4', message=FALSE, dpi=300}
mean_informed <- mean(filter(dat, type == "informed")$count)
median_informed <- median(filter(dat, type == "informed")$count)

ggplot(filter(dat, type == "informed"), aes(x = count)) +
  geom_histogram(aes(y = ..density..), fill = cbf[8], alpha = 0.5, 
                 binwidth = diff(range(dat$count)) / 15) + 
  geom_density(size = 1) + 
  geom_vline(xintercept = 123, linetype = 2, size = 1) + 
  geom_vline(xintercept = 162, linetype = 3, size = 1) + 
  geom_vline(xintercept = mean_informed, color = cbf[2], size = 1) + 
  #geom_vline(xintercept = median_informed, color = cbf[3], size = 1) + 
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlab("Estimate") + ylab("Density") + 
  xlim(range(dat$count))
```
<p class="caption">**Figure 4:** Figure caption.</p>

[Back to top]("#")

---

# Estimates' error distribution (informed)

```{r, 'figure_5', message=FALSE, dpi=300}
ggplot(filter(dat, type == "informed"), aes(x = error)) +
  geom_histogram(aes(y = ..density..), fill = cbf[8], alpha = 0.5, binwidth = diff(range(dat$error)) / 15) + 
  geom_density(size = 1) + 
  geom_vline(xintercept = abs(mean_informed - 123), color = cbf[2], size = 1) + 
  #geom_vline(xintercept = abs(median_informed - 123), color = cbf[3], size = 1) +
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlab("Error") + ylab("Density")
```
<p class="caption">**Figure 5:** Figure caption.</p>

Average estimate is better than `r 100 * sum(abs(mean_informed - 123) <= filter(dat, type == "informed")$error) / length(filter(dat, type == "informed")$count)` percent of the individual estimates. 

[Back to top]("#")

---

# Confidence vs error

```{r, 'figure_6', message=FALSE, dpi=300}
ggplot(filter(dat, type == "informed"), aes(x = conf, y = error)) +
  geom_point() + 
  geom_smooth(size = 1, method = "lm", color = cbf[3]) + 
  theme_minimal(base_size = 14) + 
  guides(fill = FALSE) + 
  xlim(0, 10) +
  xlab("Confidence") + ylab("Error")
```
<p class="caption">**Figure 6:** Figure caption.</p>

[Back to top]("#")

---

````{r, 'decon', echo=FALSE}
trash <- dbDisconnect(con)
```

